OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-03-05 paper/paper.Rmd
Update raw database seq counts

When fitting to public databases, OTU quality dropped in closed reference mode
to different degrees depending on the database and dataset source, and no more
than half of query sequences were able to be fit to OTUs across any
dataset/database combination. 
This may reflect limitations of reference
databases, which are unlikely to contain sequences from rare and novel microbes.
This drop in quality was most notable with RDP, which has only about 16,000 V4
16S sequences compared to about 170,000 in SILVA and Greengenes (**TODO: insert
R code to generate these numbers**).
We recommend that users who require an independent reference database opt for
large databases with good coverage of microbial diversity.
Since OptiClust performs faster than open reference OptiFit and creates higher
quality OTUs than closed reference OptiFit with the database strategy, we
recommend using OptiClust rather than fitting to a database whenever stable OTUs
are not required for the study at hand.

>>>>

When fitting to public databases, OTU quality dropped in closed reference mode
to different degrees depending on the database and dataset source, and no more
than half of query sequences were able to be fit to OTUs across any
dataset/database combination. 
This may reflect limitations of reference
databases, which are unlikely to contain sequences from rare and novel microbes.
This drop in quality was most notable with RDP, which contains only about 21,000
sequences compared to over 200,000 sequences in SILVA and Greengenes each at the
time of this writing.
We recommend that users who require an independent reference database opt for
large databases with good coverage of microbial diversity.
Since OptiClust performs faster than open reference OptiFit and creates higher
quality OTUs than closed reference OptiFit with the database strategy, we
recommend using OptiClust rather than fitting to a database whenever stable OTUs
are not required for the study at hand.
